%-------------------------
% Resume in Latex
% Author : Ritesh Kumar Giri
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins to ensure single page fit
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% Tighten lists to save space
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%% 

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ritesh Kumar Giri} \\ \vspace{2pt}
    \small +91-7007436164 $|$ \href{mailto:rgiri5001@gmail.com}{\underline{rgiri5001@gmail.com}} $|$ 
    \href{https://linkedin.com/in/ritesh-kumar-giri}{\underline{LinkedIn}} $|$
    \href{https://github.com/ritesh-kumar-giri}{\underline{GitHub}}
\end{center}

%-----------PROFILE SUMMARY-----------
\section{Profile}
\small{Passionate Computer Science Engineer specializing in Full-Stack Development, Artificial Intelligence (AI), and Machine Learning (ML). Proficient in architecting responsive, data-driven web applications and intelligent automation tools. Seeking opportunities as a Software Engineer or AI Developer to build scalable, innovative products.}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Babu Banarasi Das Northern India Institute of Technology}{Lucknow, India}
      {Bachelor of Technology in Computer Science \& Engineering}{2022 -- Present}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt]
    \small{\item{
     \textbf{Languages}{: C++, TypeScript, JavaScript, Python, SQL} \\
     \textbf{Frontend}{: React.js, Redux Toolkit, Next.js, HTML5, CSS3, Tailwind CSS, Framer} \\
     \textbf{Backend}{: Node.js, Express.js, Prisma, REST APIs, Socket.IO, Microservices} \\
     \textbf{Databases}{: PostgreSQL, MongoDB, Pinecone, Redis} \\
     \textbf{AI/ML}{: LangChain, Google Gemini API, Groq SDK} \\
     \textbf{DevOps \& Tools}{: Git, Docker, Kubernetes, CI/CD (GitHub Actions), Postman, VS Code}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Freelance Web Developer}{Jan 2025 -- Present}
      {NextGen Fusion}{Remote}
      \resumeItemListStart
        \resumeItem{Develop and maintain 50+ live WordPress websites and 10+ MERN Stack applications, ensuring scalable backend architectures.}
        \resumeItem{Orchestrate CI/CD pipelines using Vercel, Netlify, Render, AWS, and Hostinger for automated delivery.}
        \resumeItem{Deploy containerized production environments using Docker and Kubernetes to ensure system consistency.}
        \resumeItem{Execute end-to-end solutions including UI/UX design, secure backend APIs, and complete hosting setup.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
        {\textbf{Tat Vivah — Multi-Vendor Wedding E-Commerce Platform}}{Jan 2026 -- Feb 2026}
      \resumeItemListStart
        \resumeItem{Engineered a scalable multi-vendor E-Commerce platform using TypeScript, Node.js, PostgreSQL, and Prisma.}
        \resumeItem{Enforced Role-Based Access Control (RBAC) with JWT authentication for Buyers, Sellers, and Admins.}
        \resumeItem{Formulated real-time inventory management and atomic checkout workflows to prevent overselling.}
        \resumeItem{Optimized system performance by integrating Redis caching and adopting a layered monolith architecture.}
        \resumeItem{\textbf{Live:} \href{https://www.tatvivahtrends.com/}{tatvivahtrends.com} \quad \textbf{GitHub:} \href{https://github.com/ritesh5001/Tat_Vivah-Multi-Vendor-Ecom}{Repository}}
      \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Explore Fusion — AI-Powered Travel Microservices App}}{Dec 2025 -- Dec 2025}
      \resumeItemListStart
        \resumeItem{Architected a comprehensive travel ecosystem on a microservices architecture using Node.js and Gateway pattern.}
        \resumeItem{Embedded Groq AI SDK to power an AI Trip Planner and Travel Buddy Matcher with personalized itineraries.}
        \resumeItem{Enabled real-time bidirectional messaging using Socket.IO and React (Vite) for community interactions.}
        \resumeItem{Constructed an Instagram-style social feed, secure JWT auth, and ImageKit for optimized media handling.}
        \resumeItem{\textbf{Live:} \href{https://www.explorefusion.online/}{explorefusion.online} \quad \textbf{GitHub:} \href{https://github.com/ritesh5001/Explore-Fusion}{Repository}}
      \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{JARVIS AI — Full-Stack AI Chat Platform}}{Sept 2025 -- Dec 2025}
      \resumeItemListStart
        \resumeItem{Programmed an AI-powered chat application featuring secure JWT authentication and real-time messaging.}
        \resumeItem{Synthesized long-term conversational memory utilizing Pinecone vector database and Google Gemini API.}
        \resumeItem{Established secure REST APIs with Node.js/Express and integrated context-aware AI responses.}
        \resumeItem{\textbf{Live:} \href{https://jarvisai.riteshgiri.dev/}{jarvisai.riteshgiri.dev} \quad \textbf{GitHub:} \href{https://github.com/ritesh5001/ChatAI}{Repository}}
      \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------CERTIFICATIONS & ACHIEVEMENTS-----------
\section{Certifications \& Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt]
    \small{\item{
     \textbf{Job Ready Cohort (Sheryians Coding School)}{: Intensive Full-Stack training covering DSA, System Design, and DevOps (Docker, CI/CD).} \\
     \textbf{Data Science - AI \& DSA (ShapeMySkills)}{: Completed a 90-hour training program focusing on AI algorithms, Machine Learning, and Python.} \\
     \textbf{Achievements}{: 1st Prize Winner, Utkarsh 2022 Photography Competition; Cleared Indian Air Force Exam.} \\
     \textbf{Leadership}{: Coordinator, Discipline Team at BBDNIIT.}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
